Einstein's gravity from a polynomial affine model

### 2016-05-09 AffGR-PRD.tex
Introduction finished

Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton self-interaction is mediated by the torsion. This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it was proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
%%Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}. However, in the considered framework all graviton self-interaction is mediated by the torsion, which might allow to bypass the general postulates supporting the theorem.

The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations. % in vacuum. In addition, we show that ---in the same sector--- under the assumption of the existence of a unique non-degenerated, covariantly constant $\binom{0}{2}$-tensor, $g$ (which could be thought as a metric), the system of a scalar field coupled with the polynomial affine gravity accepts the minimally coupled Einstein--Klein--Gordon as a solution.
The paper is organized as follows. In Sec.~\ref{model}, we present briefly the polynomial affine gravity model, and summarize the results obtained in Ref.~\cite{Skirzewski:2014eta} concerning the Newtonian limit of the model. In Sec.~\ref{rlimit}, we restrict ourselves to the sector of the theory with vanishing torsion, and find the field equations; which surprisingly are a known generalization of the Einstein's field equation. Then, in Sec.~\ref{matter} we show that under certain considerations the coupling of the gravitational model with a scalar field represents a generalization of the minimally coupled system Einstein--Klein--Gordon. In Sec.~\ref{propag}, we present a brief analysis of the propagators of the model, which represent a first step toward a thorough study of the degrees of freedom of these theory. And in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results. In order to make the paper self-contained, we have included three appendices: In Appendix~\ref{DA}, we describe a dimensional analysis strategy that allowed us to build up the most general action consistent with diffeomorphisms. In Appendix~\ref{Known}, we show a collection of known solutions to the effective field equations of the model. Finally, in Appendix~\ref{Schw}, we demonstrate---restricting ourselves to the vanishing torsion sector---the equivalent of the Birkhoff's theorem of the theory.

>>>>

Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton \emph{self-interaction} is mediated by non-Riemannian parts of the connection. This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it was proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
%%Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}. However, in the considered framework all graviton self-interaction is mediated by the torsion, which might allow to bypass the general postulates supporting the theorem.

The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations. % in vacuum. In addition, we show that ---in the same sector--- under the assumption of the existence of a unique non-degenerated, covariantly constant $\binom{0}{2}$-tensor, $g$ (which could be thought as a metric), the system of a scalar field coupled with the polynomial affine gravity accepts the minimally coupled Einstein--Klein--Gordon as a solution.
The paper is organized as follows. In Sec.~\ref{model}, we present briefly the polynomial affine gravity model, and summarize the results obtained in Ref.~\cite{Skirzewski:2014eta} concerning the Newtonian limit of the model. In Sec.~\ref{rlimit}, we restrict ourselves to the sector of the theory with vanishing torsion, and find the field equations; which surprisingly are a known generalization of the Einstein's field equation. Then, in Sec.~\ref{matter} we show that under certain considerations the coupling of the gravitational model with a scalar field represents a generalization of the minimally coupled system Einstein--Klein--Gordon. In Sec.~\ref{propag}, we present a brief analysis of the propagators of the model, which allows us to count the propagating degrees of freedom. In addition, we corroborate that result with a method equivalent to the one of Dirac. And in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results. In order to make the paper self-contained, we have included three appendices: In Appendix~\ref{DA}, we describe a dimensional analysis strategy that allowed us to build up the most general action consistent with diffeomorphisms invariance. In Appendix~\ref{Known}, we show a collection of known solutions to the effective field equations of the model. Finally, in Appendix~\ref{Schw}, we demonstrate---restricting ourselves to the vanishing torsion sector---the equivalent of the Birkhoff's theorem of the theory.
